---
title: "Wrap-up exercises for Day 1 - Day 6"
date: "Day 7"
output: html_document
---

All questions should be answered by a single Rmd file that produces the answer to the question in code chunks and has text that interprets or describes the results where required.


0. Load the `dplyr` library.
```{r}

```

1. Download the mouse data set
```{r}
library(downloader) 
url <- "https://raw.githubusercontent.com/genomicsclass/dagdata/master/inst/extdata/femaleMiceWeights.csv"
filename <- "femaleMiceWeights.csv" 
download(url, destfile=filename)
```


1.  Read in the file `femaleMiceWeights.csv` as an object called `data`. What class is the object? What are the column names?
```{r}

```

2. Determine how many mice are present on the high-fat diet ('hf') and how many on normal diet ('chow'). Extract the weights of mice on a high-fat diet. What is the average weight in the high-fat group? What is their median? What is their variance?
```{r}

```

3. How would you expect the median and the mean to change if we add a mouse with weight 100 to the weight vector of the high-fat group above? Explain and test whether your conjecture was right.
```{r}

```

4. Go back to the full data of all weights (`data`). Is the Bodyweight significantly different between the two groups of mice? Perform a t-test and interpret the results. *Optional: Could it be that you made a type-I or type-II error?*
```{r}

```


5. Use a boxplot to illustrate the distribution of weights within each group. Describe how the median and the 75% quantile compare between the groups? Are outliers present in one of the groups?
```{r}

```


6. Set a seed at 1 and sample a random number from a normal distribution with mean 2 and standard deviation 0.5. Do you expect that your class mates will get the same number?
```{r}

```

7. *Optional:* Set a seed at 1 and and sample from `1:nrow(data)` a sample of size `nrow(data)`. Use this to obtain a permuted version of the weights column but keep the other columns unchanged. Are the permuted weights significantly different between the two groups of mice? Perform a t-test and interpret the results.


8. Load the following data:
```{r}
data(nym.2002, package="UsingR")
```

9. Fit a linear model of finish time on age and intepret the results. Is age a significant predictor of finish times? Are older runners faster? What is the 95% confidence interval of the coefficient of age? *Hint: Use the `summary` function to obtain details on the fitted linear model including the estimate and the standard error and note that for a normal distribution the 95% confidence interval is given by +/- 1.96 standard errors.*

```{r}

```


10. Create two separate dataframes for runner home: `MA` and `NY` and plot histograms of the finish times of each group. Which one has a higher spread?
```{r}

```


11. What is the Pearson correlation between age and finish time in each group? Make scatterplots of time versus age for each group.
```{r}

```


