---
title: "Wrap-up exercises for Day 1 - Day 6"
date: "Day 7"
output: html_document
---

All questions should be answered by a single Rmd file that produces the answer to the question in code chunks and has text that interprets or describes the results where required.


0. Load the `dplyr` library and set a seed of 1.
```{r}

```

1. Download the mouse data set
```{r}
library(downloader) 
url <- "https://raw.githubusercontent.com/genomicsclass/dagdata/master/inst/extdata/femaleMiceWeights.csv"
filename <- "femaleMiceWeights.csv" 
download(url, destfile=filename)
```


1.  Read in the file `femaleMiceWeights.csv` as an object called `data`. What class is the object? What are the column names?
```{r}

```

2. Determine how many mice are present on the high-fat fiet ('hf') and how many on normal diet ('chow'). What is the average weight in the high-fat group? What is their median?
```{r}

```


3. Is the Bodyweight significantly different between the two groups of mice? Perform a t-test and interpret the results.
```{r}

```


4. Use a boxplot to illustrate the distribution of weights within each group. Describe how the median and the 75% quantile compare between the groups? Are outliers present in the 'hf' group?
```{r}

```



Load the folowing data:
```{r}
data(nym.2002, package="UsingR")
```

5. Fit a linear model of finish time on age and intepret the results. Is age a significant predictor of finish times? Are older runners faster?

```{r}

```


6. Create two separate dataframes for runner home: `MA` and `NY` and make histograms of the finish times of each group.
```{r}

```


7. What is the Pearson correlation between age and finish time in each group? Make scatterplots of time versus age for each group?
```{r}

```


